A Survey of Real-Time Strategy Game AI\\ Research and Competition in StarCraft

### 2013-03-09 survey.tex
Commenting bios for now

\begin{IEEEbiographynophoto}{Santiago Onta\~{n}\'{o}n}
is an assistant professor in the Computer Science Department at Drexel University. His main research interests are game AI, case-based reasoning and machine learning, fields in which he has published more than 90 peer-reviewed papers. He obtained his PhD form the Autonomous University of Barcelona (UAB), Spain. Before joining Drexel University, he held postdoctoral research positions at the Artificial Intelligence Research Institute (IIIA) in Barcelona, Spain, at the Georgia Institute of Technology (GeorgiaTech) in Atlanta, USA, and at the University of Barcelona, Spain.  
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{Alberto Uriarte}
received the B.S. degree in Computer Science from Autonomous University of Barcelona (UAB), Spain, in 2006 and the M.S. degree in Computer Vision and Artificial Intelligence from Autonomous University of Barcelona (UAB), Spain, in 2011. He is currently pursuing the Ph.D. degree in computer science at Drexel University. His research interest includes game AI, RTS games, multiagents systems, procedural content generation, computational geometry, machine learning and drama management.  
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{Florian Richoux}
  is an associate  professor at the Laboratory of  Computer Science of
  the University of Nantes,  France.  His main research field concerns
  parallel  algorithms for solving  constraint-based problems  and has
  strong  interests   in  AI,  in  particular  game   AI  and  machine
  learning. He  obtained his Ph.D. in Theoretical  Computer Science at
  the {\'E}cole Polytechnique  in 2009 and has been  for three years a
  CNRS   research  fellow  at   the  Japanese-French   Laboratory  for
  Informatics of the University of Tokyo, Japan.
\end{IEEEbiographynophoto}

>>>>

% \begin{IEEEbiographynophoto}{Santiago Onta\~{n}\'{o}n}
% is an assistant professor in the Computer Science Department at Drexel University. His main research interests are game AI, case-based reasoning and machine learning, fields in which he has published more than 90 peer-reviewed papers. He obtained his PhD form the Autonomous University of Barcelona (UAB), Spain. Before joining Drexel University, he held postdoctoral research positions at the Artificial Intelligence Research Institute (IIIA) in Barcelona, Spain, at the Georgia Institute of Technology (GeorgiaTech) in Atlanta, USA, and at the University of Barcelona, Spain.  
% \end{IEEEbiographynophoto}

% \begin{IEEEbiographynophoto}{Alberto Uriarte}
% received the B.S. degree in Computer Science from Autonomous University of Barcelona (UAB), Spain, in 2006 and the M.S. degree in Computer Vision and Artificial Intelligence from Autonomous University of Barcelona (UAB), Spain, in 2011. He is currently pursuing the Ph.D. degree in computer science at Drexel University. His research interest includes game AI, RTS games, multiagents systems, procedural content generation, computational geometry, machine learning and drama management.  
% \end{IEEEbiographynophoto}

% \begin{IEEEbiographynophoto}{Florian Richoux}
%   is an associate  professor at the Laboratory of  Computer Science of
%   the University of Nantes,  France.  His main research field concerns
%   parallel  algorithms for solving  constraint-based problems  and has
%   strong  interests   in  AI,  in  particular  game   AI  and  machine
%   learning. He  obtained his Ph.D. in Theoretical  Computer Science at
%   the {\'E}cole Polytechnique  in 2009 and has been  for three years a
%   CNRS   research  fellow  at   the  Japanese-French   Laboratory  for
%   Informatics of the University of Tokyo, Japan.
% \end{IEEEbiographynophoto}
